
\Section{Introduction}
Although blockchain and other types of distributed ledgers are still in their infancy a growing number of people and companies are starting to see that they hold great promise, especially when it comes to financial technology, where things like trust and security is held to be very important. 

%https://nordic.businessinsider.com/bitcoin-history-cryptocurrency-satoshi-nakamoto-2017-12?r=US&IR=T
%https://bitcoin.org/bitcoin.pdf
%https://www.blockchain.com/sv/btc/block-height/0
%https://www.theverge.com/2013/5/6/4295028/report-satoshi-nakamoto
%bloody: https://bitcointalk.org/index.php?topic=234.msg1976#msg1976
%https://pastebin.com/syrmi3ET

%There is alot more things that could be writen here. speculations on who satoshi is, previous bitcoin like projects, why he diapeared etc...
\Subsection{The origins of bitcoin}
The most well known, developed and researched blockchain technology is know as Bitcoin. The mysterious nature of bitcoins creator makes hard to pinpoint how and when the idea was first thought up and when the development started, the most exact way and most well known would be to pinpoint at: \texttt{2009-01-03 18:15:05}, which is the timestamp on the very first block in the bitcoin blockchian, however the white paper (\textbf{Bitcoin: A Peer-to-Peer Electronic Cash System}) specifying the technical details circulated on cryptographic mailing lists as early as 31 October 2008, and the domain name \texttt{bitcoin.org} was registered 18 August 2008. 

\Subsubsection{Satoshi Nakamoto}

The author name given in the white paper is \textbf{\texttt{Satoshi Nakamoto}}, this name is believed to be a pseudonym. Satoshi remained in the bitcoin community for a couple of years. Regularly posting on the forum \texttt{bitcointalk.org} and keeping up with conversations in the mailing list. Those who have been interested in finding out Satoshi's real identity have analyzed his active time and language used. The findings were that Satoshi was most active during Western European day time, and he also used a lot of Anglo-colloquialisms such as ''bloody hard'', and ''flat'' instead of apartment, so a popular theory is that Satoshi lived in Britain at least during this time. 

\texttt{April 23, 2011} was the last time anyone ever heard from Satoshi Nakamoto, in a mail to a fellow developer Mike Hearn he said ''I've moved on to other things.  It's in good hands with Gavin and everyone.''. Speculations on who Satoshi really is still going strong even to this day, but Nakamoto's true identity is so far unknown. 
