%There is alot more things that could be writen here. speculations on who
%satoshi is, previous bitcoin like projects, why he diapeared etc...
\Section{The origins of Bitcoin}
The most well known, developed and researched blockchain technology is Bitcoin.
The mysterious nature of Bitcoins creator makes it hard to pinpoint how
and when the idea was first thought up or when the development actually started. The
most exact way would be to pinpoint at:
\texttt{2009-01-03 18:15:05}, which is the timestamp in the very
first block in the Bitcoin blockchain, however the white paper (\textbf{Bitcoin:
A Peer-to-Peer Electronic Cash System})\cite{genesis}\cite{nakamoto_bitcoin} specifying the
technical details circulated on cryptographic mailing lists as early as 31
October 2008, and the domain name \texttt{bitcoin.org} was registered 18 August
2008.\cite{bernard_2018}

\Subsection{Satoshi Nakamoto}

The author name given in the white paper is 
\textbf{\texttt{Satoshi Nakamoto}} (Often referred to by a single name, like Nakamoto or Satoshi\footnote{Not to be confused with the tiniest fraction of a bitcoin, which is always writen with a small letter: satoshi. See glossary}),
this name is believed to be a pseudonym. Nakamoto remained in the bitcoin
community for a couple of years, regularly posting on the forum
\texttt{bitcointalk.org} and keeping up with conversations in the mailing list.
Those who have been interested in finding out Nakamoto's real identity have
analyzed his active time and language used. The findings were that Nakamoto was
most active during Western European day time, and he also used a lot of
Anglo-colloquialisms such as \enquote{bloody hard} \cite{nakamoto_bloody}, and
\enquote{flat} instead of apartment, so a popular theory is that Satoshi lived in
Britain, at least during this time.\cite{bernard_2018}

\texttt{April 23, 2011} was the last time anyone ever heard from Satoshi
Nakamoto, in a mail to a fellow developer Mike Hearn he said \enquote{I've 
	moved on to other things.  It's in good hands with Gavin and everyone.}.\cite{nakamoto_last_mail}
Speculations on who Satoshi really is are still going strong even to this day, but
Nakamoto's true identity is so far unknown.\cite{bernard_2018}\cite{jeffries_2013}
