\Section{Off-chain atomic swaps}
How an on-chain atomic swap functions should be pretty clear. The script never does
anyhting I would call super complex. Off-chain atomic swaps however is a bit of
a different story and it can be pretty hard to grasp, escpecially with the
simplified explenations I have given so far. 

An off-chain atomic swap is as you might imagine an atomic swap, but if
it goes as planned it occurs entirrly without any script being executed
on the blockchain. In fact this version of an atomic swap does not use any
specialized scripts at all, instead it uses the clever mechanisms in htlc
contracts to perform it, even across chains. 

As you might remember from payment channels and lightning network 
a multi-hop transactions relies on the htlc contract to be safe. 
THe htlc contracts needs the same hashed pre-image and a strictly
decreasing timelock to be safe. This holds true even in the 
case where a multi-hop transaction travels across chains.
The requirements is that ALice and Bob run specialized 
lightning network software, that runs on both chains. And 
bot of them has to have an open channel on both cryptocurrencies.
Also there needs to be a viable path between eachother
on both networks. 

THis is perhaps best demostrated with a diagram

*Show image and explain*

\Subsection{Off-chain implementation details}
my implememtation of this used most of the same setup as the on-chain swap 
implementation, still used golang, still used the same libraries, still
used the same nodes. A new addition was the lnd library. This is a golang
specific implementation of the BOLT specification. Te BOLT specification
is the official document detailing the protocol and software that drives the 
lightning network, I will come back to this shortly.

My implementaton does not properly connect to the lightning network, doing
it that way would take to much time and it would be very likely to fail for
a newcomer such as me. Instead I implementated my own proper payment channels,
it could be seen as my own private lightning network. I did not use all the proper 
protocol stuff, as I was in controll of both nodes and I was in full control. 

The payment channels were setup using proper contracts as defined by the BOLT 
specification. THis time everything was packed into one neat program, with proper
datastructures for the simulated users and their channels. As before the program 
did not braodcast anything by it self, instead it printed the hex-formated transactions
and the user can optionally braodcast them if they want to try something.

In my tiny network only Alice and Bob existed and they had two channels between them,
one in bitcoin and one in litecoin. I implemented it so that they could make normal
transactions in the payment channels. When I got tht to function properly
I performed my first off-chain atomic swap, using the same method as I showed earlier.
It worked just as intended. I tried all outcomes and it functioned as expected.  
